HO unification from object language to meta language

### 2024-04-03 paper/main.tex
add example of pregress-eta-right from example of sec7

\newcommand{\progressetaleft}{\emph{progress-$\eta$-left}}
\begin{definition}[\progressetaleft]\label{def:progressetaleft}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$X$ becomes rigid. There are two cases:
\begin{enumerate}
  \item if $X = a$ or $X = y$ or $X = f \appsep a_1\ldots a_n$
    we unify the $\eta$-expansion of the $X$ with $T$, that is we run
    $\lambda x.X \appsep x\Ue{} T$  (under
    the context $\Gamma$)
    \noteE[inline]{where y comes from? $X = y$: $y$ is in the ctx of X}
    \item if $X = \lambda x.t$ we run $X \Ue{} T$.
\end{enumerate}
\end{definition}

\newcommand{\progressetaright}{\emph{progress-$\eta$-right}}
\begin{definition}[\progressetaright]\label{def:progressetaright} A link
\linketaM{\Gamma}{X}{T} is removed from \linkStore when either 1)
$\testmaybeeta~T$ does not hold (anymore) or 2) by $\eta$-contracting $T$ to
$T'$, $T'$ is a term not starting with the \elpiIn{lam} constructor. In the
first case, $X$ is unified with $T$ and in the second one, $X$ is unified with
$T'$ (under the context $\Gamma$).
\end{definition}

@@

We delay in next section a \linketa progression due to \progressetaright

@@

\noteD[inline]{ci vuole l'esempio per il \progressetaright}
% After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
% This assignment makes $l_2$ to progress since the \lhs is materialized and by
% unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
% y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
% After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
% \elpiIn{progress} fixpoint terminates. Next, the second unification problem is
% run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
% and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
% $Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
% As last step, the last link is progressed and the final \Ho substitution is
% $\{X _{} \mapsto \lambda x.\lambda y.x, Y _{x} \mapsto \lambda y.x, 
% G _{yx} \mapsto y, Z _{} \mapsto f~\lambda x.x, 
% H _{x} \mapsto \lambda y.y\}$.
% The decompilation phase is only charged, in this example to solve the mappings,
% since no suspended links remain. The only mapping in the list is
% \mapping{F}{H}{2}, which will assign the $F$ variable in \Fo{} to $\lambda xy.y$

>>>>

\newcommand{\progressetaleft}{\emph{progress-$\eta$-left}\xspace}
\begin{definition}[\progressetaleft]\label{def:progressetaleft}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$X$ becomes rigid. There are two cases:
\begin{enumerate}
  \item if $X = a$ or $X = y$ or $X = f \appsep a_1\ldots a_n$
    we unify the $\eta$-expansion of the $X$ with $T$, that is we run
    $\lambda x.X \appsep x\Ue{} T$  (under
    the context $\Gamma$)
    \noteE[inline]{where y comes from? $X = y$: $y$ is in the ctx of X}
    \item if $X = \lambda x.t$ we run $X \Ue{} T$.
\end{enumerate}
\end{definition}

\newcommand{\progressetaright}{\emph{progress-$\eta$-right}\xspace}
\begin{definition}[\progressetaright]\label{def:progressetaright} A link
\linketaM{\Gamma}{X}{T} is removed from \linkStore when either 1)
$\testmaybeeta~T$ does not hold (anymore) or 2) by $\eta$-contracting $T$ to
$T'$, $T'$ is a term not starting with the \elpiIn{lam} constructor. In the
first case, $X$ is unified with $T$ and in the second one, $X$ is unified with
$T'$ (under the context $\Gamma$).
\end{definition}

@@

We delay at the end of  next section an example of \linketa progression due to
\progressetaright

@@

In this example, $\hoUnifPb_1$ assigns $A$ which triggers $\linkStore_3$ and
then $\linkStore_4$ by \cref{def:progressetaleft}. $C_{yx}$ is therefore
assigned to $x$ (the second variable of its scope). We can finally see the
\progressetaright of $\linkStore_1$: its \rhs is now $\lambda y.y$ ($C_{xy}$
gives $y$). Since it is no more in \maybeeta, $\lambda y.y$ is unified with
$E_x$. Moreover, $\linkStore_2$ is also triggered due to
\cref{def:progressetaright}: $\lambda x.(f \appsep (lambda y.y) \appsep x)$ is
$\eta$-reducible to $f \appsep (lambda y.y)$ which is a term not starting with
the \elpiIn{lam} constructor.

% After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
% This assignment makes $l_2$ to progress since the \lhs is materialized and by
% unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
% y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
% After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
% \elpiIn{progress} fixpoint terminates. Next, the second unification problem is
% run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
% and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
% $Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
% As last step, the last link is progressed and the final \Ho substitution is
% $\{X _{} \mapsto \lambda x.\lambda y.x, Y _{x} \mapsto \lambda y.x, 
% G _{yx} \mapsto y, Z _{} \mapsto f~\lambda x.x, 
% H _{x} \mapsto \lambda y.y\}$.
% The decompilation phase is only charged, in this example to solve the mappings,
% since no suspended links remain. The only mapping in the list is
% \mapping{F}{H}{2}, which will assign the $F$ variable in \Fo{} to $\lambda xy.y$
